---
title: "testPipes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{testPipes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(testPipes)
```

## DESCRIPTION

This package simply aims to reproduce an error encountered while working
on a bigger [project](https://github.com/informalr/informalr/)
when using pipes (%>%).

In short,
GHA [fails](https://github.com/informalr/informalr/actions/runs/442815899)
to build on macOS and Ubuntu when pipes are used in more than one single file.

## TWO SEPARATE R FILES

This package contains two R scripts (function1.R and function2.R).

function1 cleans the dataframe given as input

```{r}
df1 <- data.frame(col1 = c(1,NA,2), col2 = c(3,NA,4))
print(df1)
function1(df1)
```

function2 also cleans the dataframe given as input

```{r}
df2 <- data.frame(col1 = c(23,24), col2 = c(25,NA))
print(df2)
function2(df2)
```


## ERROR

Pipes will be introduced into one file (function1.R) on branch pipe1file and
into two files (function1.R and function2.R) on branch pipe2files.

We expect that 
